---
title: "ForLiveSession1"
author: "Andy"
date: "1/5/2020"
output: html_document
---

### Data Science Profile barplot
```{r}
scores = c(3,2,6,7,2,7,8)
subject = c("Data Viz","Machine Learning","Mathematics","Statistics","Computer Science","Communication","Domain Expertise")
DSProfile=data.frame(Subject=subject,Scores=scores)

barplot(DSProfile$Scores, names.arg = DSProfile$Subject)
```

### Questions 2.1, 2.2, and 2.3
```{r}
population = rchisq(10000000,2,ncp=0) #note the the number of draws here
hist(population)
mean(population)
sd(population)
```

### Sampling Distribution of the Sample Mean
now make a function in which you pass the sample size, the number of samples to take #and thus the number of sample means to return as well as the mean and sd.  

Define these outside the function so that they exist outside the function (global)

xBarVec=c()

### The Function
```{r}
#####################################################
# Funciton: xbarGenerator
# Argements: samplesize: the size of the sample that each sample mean is based on. 
#            number_of_samples: the number of samples and thus sample means we will generate
# Author: Bivin Sadler
#####################################################
xbarGenerator = function(sampleSize = 30,number_of_samples = 100)
{
  for(i in 1:number_of_samples)
  {
    theSample = sample(population,sampleSize)
    xbar = mean(theSample)
    xBarVec = c(xBarVec, xbar)
  }
  return(xBarVec)
}
```


### Questions 2.4 and 2.5
```{r}
xBarVec = c() #global vector to hold the sample means
#####################################################
# Funciton: xbarGenerator (Adpated)
# Argements: samplesize: the size of the sample that each sample mean is based on. 
#            number_of_samples: the number of samples and thus sample means we will generate
# Author: Bivin Sadler
#####################################################
xbarGenerator2 = function(sampleSize = 30,number_of_samples = 100, mean = 0, sd = 1)
{
  for(i in 1:number_of_samples)
  {
    theSample = rnorm(sampleSize,mean,sd)
    xbar = mean(theSample)
    xBarVec = c(xBarVec, xbar)
  }
  return(xBarVec)
}

xbars = xbarGenerator2(60,1000,50,10)
hist(xbars)
summary(xbars)
sd(xbars)
10/sqrt(60)
```


###Question 3
Patrons = c(25,19,37,29,40,28,31)
t.test(Patrons,mu=21)
t.critical=qt(0.975,6)